---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adm

<!-- badges: start -->
<!-- badges: end -->

The goal of adm is to **a**utomate **d**ata **m**odels created with the
[dm](https://CRAN.R-project.org/package=dm) package. It guesses primary and
foreign keys assuming the names of the tables and keys follow two rules:

1. For each table, the primary key has the same name as the table with the
prefix `_id`. For example the table `x` has a primary key named `x_id`.

2. If an `_id` column exists in a table which name is different than the prefix
of that `_id` column, then that column is a foreign key linking to another
table. For example, in the table `x_id`, the column `y_id` is a foreign key
linking to the table `y`.

## Installation

You can install the development version of adm from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/adm")
```

## Example

```{r example}
library(adm)

x <- data.frame(x_id = 1, y_id = 2)
y <- data.frame(y_id = 2)
dm <- dm::dm(x, y) |>
  add_keys()

dm::dm_draw(dm)
```

